### 2015-02-16 paper_40_mpi.tex
a lot more work on satisfaction

            Surveys are used to measure satisfaction for MPI.  A series of questions will
            be presented to all or a subset of the customers.  Any customer that chooses
            to respond to the survey is considered a respondent.  A respondent can rate
            questions with a numerical response where the minimum value indicates maximum
            disagreement and the maximum value indicates
            the maximum agreement. Common rating scales would be
            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
            \ref{tab:samplesurvey}.

            \begin{longtable}{@{}l rr rr}
                \toprule%
                 \centering%
                 {\bfseries ID}
                 & {\bfseries Question}
                 & {\bfseries Disagree}
                 & {\bfseries Neutral}
                 & {\bfseries Agree}  \\

@@

            \paragraph{ISSUES WITH SURVEYS}

                There are 2 cases of surveys that could be used for satisfaction.  First is when an SDO is part of a larger organization.  Typically there are a small number of business partners that help to guide and direct the work performed by the SDO.  In this case, the business partners are the ones offering survey responses and they should all be willing to respond.  Thus, those business partners represent the entire population, and the surveys should result in a 100\% response rate which is technically a census.  
         The only bias that will be present here is the bias of the business partners and sampling cannot control for that.

       In the other case, end-users will be surveyed for satisfaction. Obviously, the entire population cannot be surveyed, so a probability sample should be randomly created. Even then, bias will be present.  First, not all users will respond.  This is because survey respondents tend to sit at the extremes of either satisfied or dissatisfied.  Thus the results will tend to indicate that separation. Second, even with probability  sampling it is possible to miss entire groups of population members. For example consider a banking application such as a savings account, a survey would most likely be presented online and it would have a coverage bias due the exclusion of savings account holders that do not bank online.  Third, a selection bias can occur when some members of the population have a higher probability of inclusion in the sampling frame than others.  One example could be a user with multiple savings accounts.  The selection bias is typically easy to avoid if the bias is identified.  Weighting is a common solution here.

            The questions  are answered on a scale of 1 to 5 with 1 being 
            \textbf{Strongly Misses Expectations} and 5 being \textbf{Strongly Exceeds
            Expectations}.

            \paragraph{SATISFACTION DATA}
                \begin{longtable}{@{}l rr rr}
                    \toprule%
                     \centering%
                     {\bfseries Column Name}
                     & {\bfseries Data Type}
                     &  \\

@@

                    \caption{SATISFACTION DATA NEEDED FOR MPI}
                    \label{tab:satisfaction}
                \end{longtable}

            \paragraph{SATISFACTION FORMULA}

            The following is an algorithm to calculate the satisfaction of software.
            \[
                S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
            \]

>>>>

            Surveys are used to measure satisfaction for MPI.  A series of statements will
            be presented to all or a subset of the customers.  Any customer that chooses
            to respond to the survey is considered a respondent.  A respondent can rate
            statements based upon a Likert Scale\footnote{"The Likert Scale presents 
            respondents with a series of (attitude) dimensions, which fall along a
            continuum." \cite{Cowles2015}} with a numerical response where the 
            minimum value indicates maximum
            disagreement and the maximum value indicates
            the maximum agreement. Common rating scales would be
            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
            \ref{tab:samplesurvey}.

            \begin{longtable}{@{}l rr rr}
                \toprule%
                 \centering%
                 {\bfseries ID}
                 & {\bfseries Statement}
                 & {\bfseries Disagree}
                 & {\bfseries Neutral}
                 & {\bfseries Agree}  \\

@@

            \paragraph{ISSUES WITH SURVEYS}
                Surveys present a number of challenges that need to be presented and briefly
                discussed.  Here are some of the issues that need to be addressed when
                using surveys.

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statments
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets os customers need to be presented with a survery.  
                    In the case of MPI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

                    \item[Second] End-users will be surveyed for satisfaction. Obviously, the 
                    entire population cannot be surveyed, so a probability sample should 
                    be randomly created. Even then, bias will be present.  
                        \begin{itemize}
                            \item Not all users will respond.  This is because survey 
                                respondents tend to sit at the extremes of either 
                                satisfied or dissatisfied.  Thus the results will tend 
                                to indicate that separation. 
                            \item  Even with probability sampling it is possible to miss 
                                entire groups of population members. For example consider a 
                                banking application such as a savings account, a survey would 
                                most likely be presented online and it would have a coverage 
                                bias due the exclusion of savings account holders that 
                                do not bank online.
                            \item A selection bias can occur when some members of the 
                                population have a higher probability of inclusion in 
                                the sampling frame than others.  One example could be 
                                a user with multiple savings accounts.  The selection 
                                bias is typically easy to avoid if the bias is 
                                identified.  Weighting is a common solution for selection bias. 
                        \end{itemize}

                    \end{description}

                \end{description}

            For more on creating appropriate surveys, see \cite{Snijkers2013} by Snijkers,
            Haraldsen, Jones, and Willimack. In the book, Snijkers et al. present a framework
            named generic statistical business process model (GSBPM) for conducting surveys
            in a business or organizational setting.  GSBPM covers the issues above as well
            as a few more issues such as response storage and risks.  Also, Cowles and Nelson
            provide another good resource for preparing and conducting surveys 
            \cite{Cowles2015}.  They even include an entire chapters on both writing 
            survey questions and survey errors.

            \paragraph{SATISFACTION DATA}
                Once the surveys have been distributed and the results collected, Table
                \ref{tab:satisfactiondata} displays the data that needs to be collected 
                in order to calculate the satisfaction element score for MPI.
                \begin{longtable}{@{}l rr rr}
                    \toprule%
                     \centering%
                     {\bfseries Column Name}
                     & {\bfseries Data Type}
                     &  \\

@@

                    \caption{SATISFACTION DATA NEEDED FOR MPI}
                    \label{tab:satisfactiondata}
                \end{longtable}

            \paragraph{SATISFACTION FORMULA}
                After collecting the necessary survey data from Table \ref{tab:satisfactiondata},
                calculating the score is rather straight forward.
                The scores for each question are averaged and then those
                values are averaged together.  If some survey questions
                are more important than others, the formula could be
                easily modified to include weighting.

                Mathematically, the following is an algorithm to calculate the 
                satisfaction element score
                of MPI.
                \[
                    S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
                \]
